DraftOne

### 2017-03-22 writing/DraftOne.Rmd
Meeting 3/21

n<- c(5, 10, 20)

#Getting list of data frames with date, x, outcome for each run
rep_df <- n %>% map(create_sims, n_reps=n_reps, central=central, sd=sd, 
                        exposure_type=exposure_type,
                        exposure_trend=exposure_trend,exposure_amp=exposure_amp,
                        average_outcome=average_outcome,outcome_trend=outcome_trend,
                        outcome_amp = outcome_amp, rr=rr, start.date = start.date)
rep_df

@@

rep_df <- n %>% map(create_sims, n_reps=3, central=100, sd=10, 
                        exposure_type = "continuous",
                        exposure_trend= "cos1",exposure_amp=.6,
                        average_outcome=22,outcome_trend="no trend",
                        outcome_amp = .6, rr=1.1, start.date = "2000-01-01")
rep_df
#This works, but why are the outcomes crazy? Oh noooooooo :( 
```

>>>>

n<- 100

#Getting list of data frames with date, x, outcome for each run
rep_df <- n %>% purrr::map(create_sims, n_reps=n_reps, central=central, sd=sd, 
                        exposure_type=exposure_type,
                        exposure_trend=exposure_trend,exposure_amp=exposure_amp,
                        average_outcome=average_outcome,outcome_trend=outcome_trend,
                        outcome_amp = outcome_amp, rr=rr, start.date = start.date)
rep_df

@@

rep_df <- n %>% purrr::map(create_sims, n_reps=3, central=100, sd=10, 
                        exposure_type = "continuous",
                        exposure_trend= "cos1",exposure_amp=.6,
                        average_outcome=22,outcome_trend="no trend",
                        outcome_amp = .6, rr=1.01, start.date = "2000-01-01")
rep_df

#This works, but why are the outcomes crazy? Oh noooooooo :( 
```
